### 2018-06-28 Sections/protocols_for_the_quantum_internet.tex
Figure reformatting to make double column, rather than stacked
mdframed
Minor corrections

\begin{figure}[!htb]
\includegraphics[width=0.375\textwidth]{SPDC_multiplexing_arch}\index{Multiplexed single-photon sources}
\caption{Quasi-deterministic single photon state preparation using $N$-fold multiplexing of heralded SPDC sources (or any other non-deterministic, but heralded source). All $N$ SPDC sources are triggered simultaneously. The heralding detectors feedforward to the multiplexer, which routes a successfully heralded single photon state (if there is one) to the output mode. With a sufficiently large bank of sources in parallel, the probability of successfully preparing a single photon state approaches unity.} \label{fig:SPDC_multiplexing_arch}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.375\textwidth]{SPDC_time_multiplexing}
\caption{Multiplexed single-photon state preparation in the temporal domain. An SPDC source operating at high repetition rate, with time-bin separation $\tau$, enters a fibre-loop with an in/out coupling switch classically controlled by the heralding outcomes. The fibre-loop acts as a quantum memory, keeping the most recent successfully heralded time-bin in memory until the procedure terminates. The output is a pulse-train where the last time-bin closely approximates a single-photon.} \label{fig:SPDC_time_multiplexing}
\end{figure}

@@

The former is experimentally straightforward, but plagued by loss, and is only suitable over short timescales, on the order of nanoseconds. The latter is more experimentally challenging, but can achieve longer storage times, limited by the lifetime ($T_1$- and $T_2$-times) of the non-optical system. For some physical systems, this can be very high, on the order of milliseconds for atomic ensemble qubits \cite{bib:Duan01, bib:Duan02, bib:LauratKimble07}, for example, which is typically adequate for the purposes of waiting out network bottlenecks.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function RandomBit():
\begin{enumerate}
    \item Prepare the equal superposition state,
    \begin{align}
    \ket\psi_\text{in} = \ket{+} = \frac{1}{\sqrt{2}}(\ket{0}+\ket{1}).
    \end{align}
    \item Most commonly this is in the polarisation basis,
    \begin{align}
    \ket{H}&\equiv\ket{0}, \nonumber \\
    \ket{V}&\equiv\ket{1}.
    \end{align}
    \item Measure the state in the logical basis, with measurement projectors,
    \begin{align}
    \hat\Pi_0 &= \ket{0}\bra{0}, \nonumber \\
    \hat\Pi_1 &= \ket{1}\bra{1}.
    \end{align}
    \item The measurement outcomes occur with probabilities,
    \begin{align}
    P_0&=|\langle 0|+\rangle|^2 = \frac{1}{2}, \nonumber \\
    P_1&=|\langle 1|+\rangle|^2 = \frac{1}{2},
    \end{align}
    following a uniform, random, binary distribution.
    \item Repeat for as many random bits as are required.
    \item $\Box$
\end{enumerate}}}}
\caption{Procedure for the generation of random bit-strings. Assuming the device is perfectly implementing this procedure, we will measure a perfect random 50/50 distribution between the two measurement outcomes. Note that the procedure requires no quantum interference, and no entanglement. Only single-qubit state preparation and measurement are required. Thus, a single-photon source, wave-plate, polarisation filter, and photo-detector are sufficient for its realisation. Favourably, if the detector is inefficient it simply reduces the bit-rate, but does not compromise the randomness of the distribution.} \label{alg:random_number}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function StateTeleportation($\ket\phi_{A_1}$, $\ket{\Phi^+}_{A_2,B}$):
\begin{enumerate}
    \item Alice prepares the state $\ket\phi_{A_1}$, which she would like to teleport to Bob.
    \item Alice and Bob share the Bell-pair $\ket{\Phi^+}_{A_2,B}$.
    \item Alice performs a Bell state projection between qubits $A_1$ and $A_2$.
    \item Alice communicates the classical measurement outcome to Bob - one of four outcomes.
    \item Bob applies an appropriate local correction to his qubit - some combination of the Pauli operators $\hat{X}$ and $\hat{Z}$ - according to the classical measurement outcome:
    \begin{align}
    \ket{\Psi^+}\bra{\Psi^+} &\to \hat{\mathbb{I}}, \nonumber \\
    \ket{\Psi^-}\bra{\Psi^-} &\to \hat{Z}, \nonumber \\
    \ket{\Phi^+}\bra{\Phi^+} &\to \hat{X}, \nonumber \\
    \ket{\Phi^-}\bra{\Phi^-} &\to \hat{Z}\hat{X}.
    \end{align}
    \item Bob is left with the state $\ket\phi_B$.
    \item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\ket\phi} & \qw & \multimeasureD{1}{\text{Bell}} & \cw  & \control \cw \\
    \lstick{} & \qw & \ghost{\text{Bell}} & \control \cw & \cwx \\
    \lstick{} & \qw & \qw & \gate{X} \cwx & \gate{Z} \cwx & \qw & \qw & \ket\phi
    \inputgroupv{2}{3}{.8em}{.8em}{\ket{\Phi^+}}
} \nonumber
\end{align}
}}
\caption{Quantum state teleportation of a single qubit.} \label{alg:state_teleport}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function GateTeleportation($\ket\psi_A\ket\phi_B$):\
\begin{enumerate}
\item We wish to apply a CNOT gate to \mbox{$\ket\psi_{A}\ket\phi_{B}$}.
\item Introduce two additional qubits, $C$ and $D$.
\item Teleport states \mbox{$\ket\psi_{A}\to\ket\psi_C$}, \mbox{$\ket\psi_{B}\to\ket\psi_D$}.
\item Apply \mbox{$\hat{\text{CNOT}} \ket \psi_C \ket\phi_D$}.
\begin{align}
\Qcircuit @C=1em @R=1.6em {
\lstick{\ket\psi} & \qw & \multimeasureD{1}{\text{Bell}} & \cw  & \control \cw \\
\lstick{} & \qw & \ghost{\text{Bell}} & \control \cw & \cwx \\
\lstick{} & \qw & \qw & \gate{X} \cwx & \gate{Z} \cwx & \ctrl{1} & \qw & \qw & \qw \inputgroupv{2}{3}{.8em}{.8em}{\ket{\Phi^+}} \\
\lstick{} & \qw & \qw & \gate{X} & \gate{Z} & \targ & \qw & \qw & \qw \inputgroupv{4}{5}{.8em}{.8em}{\ket{\Phi^+}} \\
\lstick{} & \qw & \multimeasureD{1}{\text{Bell}} & \control \cw \cwx & \cwx \\
\lstick{\ket\phi} & \qw & \ghost{\text{Bell}} & \cw  & \control \cw \cwx
} \nonumber
\end{align}
\item The CNOT is a Clifford gate and can therefore be commuted to the front of the Pauli operators to yield a CNOT followed by some different configuration of Pauli operators.
\item The CNOT now acts jointly upon the Bell-pairs that were acting as a resource for the state teleportation, independent of \mbox{$\ket\psi_{A}\ket\phi_{B}$}.
\item Group the CNOT gate and Bell-pairs together, and treat them as a 4-qubit resource state preparation stage, which does not depend on \mbox{$\ket\psi_{A}\ket\phi_{B}$}. 
\item Prepare the 4-qubit resource state, \mbox{$\ket\chi=\hat{\text{CNOT}}_{2,3}\ket{\Psi^+}_{1,2}\ket{\Psi^+}_{3,4}$}, offline in advance.
\item If the CNOT is non-deterministic, employ \textsc{Repeat Until Success} to prepare $\ket\chi$.
\item The output state is \mbox{$\hat{\text{CNOT}}_{C,D} \ket\psi_{C}\ket\phi_{D}$}.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
\lstick{\ket\psi} & \qw & \multimeasureD{1}{\text{Bell}} & \cw & \cw & \control \cw \\
\lstick{} & \qw & \ghost{\text{Bell}} & \cw & \cw & \cw \cwx & \control \cw \\
\lstick{} & \qw & \qw & \gate{X} & \gate{Z} & \qw \cwx & \gate{Z} \cwx & \qw & \qw & \qw \\
\lstick{} & \qw & \qw & \gate{X} \cwx & \qw \cwx & \gate{X} \cwx & \gate{Z} \cwx & \qw & \qw & \qw \\
\lstick{} & \qw & \multimeasureD{1}{\text{Bell}} & \control \cw \cwx & \cwx \inputgroupv{2}{5}{0.8em}{4.1em}{\ket{\chi}} \\
\lstick{\ket\phi} & \qw & \ghost{\text{Bell}} & \cw  & \control \cw \cwx
} \nonumber
\end{align}
}}
\caption{Teleporting a CNOT gate onto a 2-qubit state.} \label{alg:gate_teleport}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function EntanglementSwapping($\ket{\Phi^+}_{A_1,A_2}, \ket{\Phi^+}_{B_1,B_2}$):
\begin{enumerate}
    \item Alice locally prepares the Bell-pair,
    \begin{align}
    \ket{\Phi^+}_{A_1,A_2}.
    \end{align}
    \item Bob locally prepares the Bell-pair,
    \begin{align}
    \ket{\Phi^+}_{B_1,B_2}.
    \end{align}
    \item The net initial state is,
    \begin{align}
    \ket\psi_\text{in} = \ket{\Phi^+}_{A_1,A_2} \ket{\Phi^+}_{B_1,B_2}.
    \end{align}
    \item Alice sends qubit $A_1$ to third party Eve.
    \item Bob Sends qubit $B_1$ to third party Eve.
    \item Eve performs a Bell projection between $A_1$ and $B_1$, yielding,
    \begin{align}
    \bra{\Phi^+}_{A_1,B_1} \ket\psi_\text{in} = \ket{\Phi^+}_{A_2,B_2}.
    \end{align}
    \item In the case of the other Bell projection outcomes ($\bra{\Phi^-}_{A_1,B_1}$, $\bra{\Psi^+}_{A_1,B_1}$ or $\bra{\Psi^-}_{A_1,B_1}$), local corrections (Pauli operators) are made by Alice and/or Bob, as dictated by classical communication from Eve,
    \begin{align}
    \bra{\Phi^+}_{A_1,B_1} \ket\psi_\text{in} &= \ket{\Phi^+}_{A_2,B_2}, \nonumber \\
    \bra{\Phi^-}_{A_1,B_1} \ket\psi_\text{in} &= \hat{Z}_{B_2} \ket{\Phi^+}_{A_2,B_2}, \nonumber \\
    \bra{\Psi^+}_{A_1,B_1} \ket\psi_\text{in} &= \hat{X}_{B_2} \ket{\Phi^+}_{A_2,B_2}, \nonumber \\
    \bra{\Psi^-}_{A_1,B_1} \ket\psi_\text{in} &= \hat{X}_{B_2} \hat{Z}_{B_2} \ket{\Phi^+}_{A_2,B_2}.
    \end{align}
    \item Alice and Bob now possess a joint Bell-pair between qubits $A_2$ and $B_2$,
    \begin{align}
    \ket\psi_\text{out} = \ket{\Phi^+}_{A_2,B_2}.
    \end{align}
    \item $\Box$ \\
\end{enumerate}}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{} & \qw & \qw & \qw & \qw & \qw & \qw \\
    \lstick{} & \qw & \multimeasureD{1}{\text{Bell}} & \cw  & \control \cw
    \inputgroupv{1}{2}{.8em}{.8em}{\ket{\Phi^+}} \\
    \lstick{} & \qw & \ghost{\text{Bell}} & \control \cw & \cwx \\
    \lstick{} & \qw & \qw & \gate{X} \cwx & \gate{Z} \cwx & \qw & \qw
    \inputgroupv{3}{4}{.8em}{.8em}{\ket{\Phi^+}}
} \nonumber
\end{align}
}}
\caption{Entanglement swapping protocol between two parties. Two Bell-pairs held locally by two users, \mbox{$\ket{\Phi^+}_{A_1,A_2}\ket{\Phi^+}_{B_1,B_2}$}, are converted to a single Bell-pair shared between the users, $\ket{\Phi^+}_{A_2,B_2}$.} \label{alg:ent_swap}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function SuperdenseCoding($\ket{B_{00}}$, $x$):
\begin{enumerate}
\item Alice and Bob share the Bell-pair $\ket{B_{00}}$.
\item Alice encodes the two-bit string \mbox{$x\in\{0,1\}^2$} into a choice of the four possible Bell-pairs.
\item Alice prepares the respective Bell-pair using operations local to only her half of the shared state ($\hat{\mathbb{I}}$, $\hat{X}$, $\hat{Z}$ or \mbox{$\hat{Z}\hat{X}$}).
\item Alice sends her qubit to Bob.
\item Bob measures in the Bell basis, with four possible measurement outcomes.
\item The measurement outcome corresponds to the bit-string $x$.
\item $\Box$
\end{enumerate}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
\lstick{x_0} & \cw & \cw & \control \cw \\
\lstick{x_1} & \cw & \control \cw \\
\lstick{} & \qw & \gate{X} \cwx & \gate{Z} \cwx[-2] & \qw & \multimeasureD{1}{\text{Bell}} & \cw & \rstick{x_0} \\
\lstick{} & \qw & \qw & \qw & \qw & \ghost{\text{Bell}} & \cw & \rstick{x_1}
\inputgroupv{3}{4}{.8em}{.8em}{\ket{B_{00}}\quad} \\
} \nonumber
\end{align}
}}}
\caption{Superdense coding protocol for communicating two classical bits via transmission of a single qubit. The protocol requires the two parties share a Bell-pair as a resource, provided by a third party.} \label{alg:superdense}
\end{table}

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.38\textwidth]{SPDC_multiplexing_arch}\index{Multiplexed single-photon sources}
\caption{Quasi-deterministic single photon state preparation using $N$-fold multiplexing of heralded SPDC sources (or any other non-deterministic, but heralded source). All $N$ SPDC sources are triggered simultaneously. The heralding detectors feedforward to the multiplexer, which routes a successfully heralded single photon state (if there is one) to the output mode. With a sufficiently large bank of sources in parallel, the probability of successfully preparing a single photon state approaches unity.} \label{fig:SPDC_multiplexing_arch}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{SPDC_time_multiplexing}
\caption{Multiplexed single-photon state preparation in the temporal domain. An SPDC source operating at high repetition rate, with time-bin separation $\tau$, enters a fibre-loop with an in/out coupling switch classically controlled by the heralding outcomes. The fibre-loop acts as a quantum memory, keeping the most recent successfully heralded time-bin in memory until the procedure terminates. The output is a pulse-train where the last time-bin closely approximates a single-photon.} \label{fig:SPDC_time_multiplexing}
\end{figure}

@@

The former is experimentally straightforward, but plagued by loss, and is only suitable over short timescales, on the order of nanoseconds. The latter is more experimentally challenging, but can achieve longer storage times, limited by the lifetime ($\tau_1$- and $\tau_2$-times) of the non-optical system. For some physical systems, this can be very high, on the order of milliseconds for atomic ensemble qubits \cite{bib:Duan01, bib:Duan02, bib:LauratKimble07}, for example, which is typically adequate for the purposes of waiting out network bottlenecks.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function RandomBit():
\begin{enumerate}
    \item Prepare the equal superposition state,
    \begin{align}
    \ket\psi_\text{in} = \ket{+} = \frac{1}{\sqrt{2}}(\ket{0}+\ket{1}).
    \end{align}
    \item Most commonly this is in the polarisation basis,
    \begin{align}
    \ket{H}&\equiv\ket{0}, \nonumber \\
    \ket{V}&\equiv\ket{1}.
    \end{align}
    \item Measure the state in the logical basis, with measurement projectors,
    \begin{align}
    \hat\Pi_0 &= \ket{0}\bra{0}, \nonumber \\
    \hat\Pi_1 &= \ket{1}\bra{1}.
    \end{align}
    \item The measurement outcomes occur with probabilities,
    \begin{align}
    P_0&=|\langle 0|+\rangle|^2 = \frac{1}{2}, \nonumber \\
    P_1&=|\langle 1|+\rangle|^2 = \frac{1}{2},
    \end{align}
    following a uniform, random, binary distribution.
    \item Repeat for as many random bits as are required.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{Procedure for the generation of random bit-strings. Assuming the device is perfectly implementing this procedure, we will measure a perfect random 50/50 distribution between the two measurement outcomes. Note that the procedure requires no quantum interference, and no entanglement. Only single-qubit state preparation and measurement are required. Thus, a single-photon source, wave-plate, polarisation filter, and photo-detector are sufficient for its realisation. Favourably, if the detector is inefficient it simply reduces the bit-rate, but does not compromise the randomness of the distribution.} \label{alg:random_number}
\end{table}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function StateTeleportation($\ket\phi_{A_1}$, $\ket{\Phi^+}_{A_2,B}$):
\begin{enumerate}
    \item Alice prepares the state $\ket\phi_{A_1}$, which she would like to teleport to Bob.
    \item Alice and Bob share the Bell-pair $\ket{\Phi^+}_{A_2,B}$.
    \item Alice performs a Bell state projection between qubits $A_1$ and $A_2$.
    \item Alice communicates the classical measurement outcome to Bob - one of four outcomes.
    \item Bob applies an appropriate local correction to his qubit - some combination of the Pauli operators $\hat{X}$ and $\hat{Z}$ - according to the classical measurement outcome:
    \begin{align}
    \ket{\Psi^+}\bra{\Psi^+} &\to \hat{\mathbb{I}}, \nonumber \\
    \ket{\Psi^-}\bra{\Psi^-} &\to \hat{Z}, \nonumber \\
    \ket{\Phi^+}\bra{\Phi^+} &\to \hat{X}, \nonumber \\
    \ket{\Phi^-}\bra{\Phi^-} &\to \hat{Z}\hat{X}.
    \end{align}
    \item Bob is left with the state $\ket\phi_B$.
    \item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\ket\phi} & \qw & \multimeasureD{1}{\text{Bell}} & \cw  & \control \cw \\
    \lstick{} & \qw & \ghost{\text{Bell}} & \control \cw & \cwx \\
    \lstick{} & \qw & \qw & \gate{X} \cwx & \gate{Z} \cwx & \qw & \qw & \ket\phi
    \inputgroupv{2}{3}{.8em}{.8em}{\ket{\Phi^+}}
} \nonumber
\end{align}
\end{mdframed}
\caption{Quantum state teleportation of a single qubit.} \label{alg:state_teleport}
\end{table}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function GateTeleportation($\ket\psi_A\ket\phi_B$):\
\begin{enumerate}
\item We wish to apply a CNOT gate to \mbox{$\ket\psi_{A}\ket\phi_{B}$}.
\item Introduce two additional qubits, $C$ and $D$.
\item Teleport states \mbox{$\ket\psi_{A}\to\ket\psi_C$}, \mbox{$\ket\psi_{B}\to\ket\psi_D$}.
\item Apply \mbox{$\hat{\text{CNOT}} \ket \psi_C \ket\phi_D$}.
\begin{align}
\Qcircuit @C=1em @R=1.6em {
\lstick{\ket\psi} & \qw & \multimeasureD{1}{\text{Bell}} & \cw  & \control \cw \\
\lstick{} & \qw & \ghost{\text{Bell}} & \control \cw & \cwx \\
\lstick{} & \qw & \qw & \gate{X} \cwx & \gate{Z} \cwx & \ctrl{1} & \qw & \qw & \qw \inputgroupv{2}{3}{.8em}{.8em}{\ket{\Phi^+}} \\
\lstick{} & \qw & \qw & \gate{X} & \gate{Z} & \targ & \qw & \qw & \qw \inputgroupv{4}{5}{.8em}{.8em}{\ket{\Phi^+}} \\
\lstick{} & \qw & \multimeasureD{1}{\text{Bell}} & \control \cw \cwx & \cwx \\
\lstick{\ket\phi} & \qw & \ghost{\text{Bell}} & \cw  & \control \cw \cwx
} \nonumber
\end{align}
\item The CNOT is a Clifford gate and can therefore be commuted to the front of the Pauli operators to yield a CNOT followed by some different configuration of Pauli operators.
\item The CNOT now acts jointly upon the Bell-pairs that were acting as a resource for the state teleportation, independent of \mbox{$\ket\psi_{A}\ket\phi_{B}$}.
\item Group the CNOT gate and Bell-pairs together, and treat them as a 4-qubit resource state preparation stage, which does not depend on \mbox{$\ket\psi_{A}\ket\phi_{B}$}. 
\item Prepare the 4-qubit resource state, \mbox{$\ket\chi=\hat{\text{CNOT}}_{2,3}\ket{\Psi^+}_{1,2}\ket{\Psi^+}_{3,4}$}, offline in advance.
\item If the CNOT is non-deterministic, employ \textsc{Repeat Until Success} to prepare $\ket\chi$.
\item The output state is \mbox{$\hat{\text{CNOT}}_{C,D} \ket\psi_{C}\ket\phi_{D}$}.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
\lstick{\ket\psi} & \qw & \multimeasureD{1}{\text{Bell}} & \cw & \cw & \control \cw \\
\lstick{} & \qw & \ghost{\text{Bell}} & \cw & \cw & \cw \cwx & \control \cw \\
\lstick{} & \qw & \qw & \gate{X} & \gate{Z} & \qw \cwx & \gate{Z} \cwx & \qw & \qw & \qw \\
\lstick{} & \qw & \qw & \gate{X} \cwx & \qw \cwx & \gate{X} \cwx & \gate{Z} \cwx & \qw & \qw & \qw \\
\lstick{} & \qw & \multimeasureD{1}{\text{Bell}} & \control \cw \cwx & \cwx \inputgroupv{2}{5}{0.8em}{4.1em}{\ket{\chi}} \\
\lstick{\ket\phi} & \qw & \ghost{\text{Bell}} & \cw  & \control \cw \cwx
} \nonumber
\end{align}
\end{mdframed}
\caption{Teleporting a CNOT gate onto a 2-qubit state.} \label{alg:gate_teleport}
\end{table}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function EntanglementSwapping($\ket{\Phi^+}_{A_1,A_2}, \ket{\Phi^+}_{B_1,B_2}$):
\begin{enumerate}
    \item Alice locally prepares the Bell-pair,
    \begin{align}
    \ket{\Phi^+}_{A_1,A_2}.
    \end{align}
    \item Bob locally prepares the Bell-pair,
    \begin{align}
    \ket{\Phi^+}_{B_1,B_2}.
    \end{align}
    \item The net initial state is,
    \begin{align}
    \ket\psi_\text{in} = \ket{\Phi^+}_{A_1,A_2} \ket{\Phi^+}_{B_1,B_2}.
    \end{align}
    \item Alice sends qubit $A_1$ to third party Eve.
    \item Bob Sends qubit $B_1$ to third party Eve.
    \item Eve performs a Bell projection between $A_1$ and $B_1$, yielding,
    \begin{align}
    \bra{\Phi^+}_{A_1,B_1} \ket\psi_\text{in} = \ket{\Phi^+}_{A_2,B_2}.
    \end{align}
    \item In the case of the other Bell projection outcomes ($\bra{\Phi^-}_{A_1,B_1}$, $\bra{\Psi^+}_{A_1,B_1}$ or $\bra{\Psi^-}_{A_1,B_1}$), local corrections (Pauli operators) are made by Alice and/or Bob, as dictated by classical communication from Eve,
    \begin{align}
    \bra{\Phi^+}_{A_1,B_1} \ket\psi_\text{in} &= \ket{\Phi^+}_{A_2,B_2}, \nonumber \\
    \bra{\Phi^-}_{A_1,B_1} \ket\psi_\text{in} &= \hat{Z}_{B_2} \ket{\Phi^+}_{A_2,B_2}, \nonumber \\
    \bra{\Psi^+}_{A_1,B_1} \ket\psi_\text{in} &= \hat{X}_{B_2} \ket{\Phi^+}_{A_2,B_2}, \nonumber \\
    \bra{\Psi^-}_{A_1,B_1} \ket\psi_\text{in} &= \hat{X}_{B_2} \hat{Z}_{B_2} \ket{\Phi^+}_{A_2,B_2}.
    \end{align}
    \item Alice and Bob now possess a joint Bell-pair between qubits $A_2$ and $B_2$,
    \begin{align}
    \ket\psi_\text{out} = \ket{\Phi^+}_{A_2,B_2}.
    \end{align}
    \item $\Box$ \\
\end{enumerate}}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{} & \qw & \qw & \qw & \qw & \qw & \qw \\
    \lstick{} & \qw & \multimeasureD{1}{\text{Bell}} & \cw  & \control \cw
    \inputgroupv{1}{2}{.8em}{.8em}{\ket{\Phi^+}} \\
    \lstick{} & \qw & \ghost{\text{Bell}} & \control \cw & \cwx \\
    \lstick{} & \qw & \qw & \gate{X} \cwx & \gate{Z} \cwx & \qw & \qw
    \inputgroupv{3}{4}{.8em}{.8em}{\ket{\Phi^+}}
} \nonumber
\end{align}
\end{mdframed}
\caption{Entanglement swapping protocol between two parties. Two Bell-pairs held locally by two users, \mbox{$\ket{\Phi^+}_{A_1,A_2}\ket{\Phi^+}_{B_1,B_2}$}, are converted to a single Bell-pair shared between the users, $\ket{\Phi^+}_{A_2,B_2}$.} \label{alg:ent_swap}
\end{table}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function SuperdenseCoding($\ket{B_{00}}$, $x$):
\begin{enumerate}
\item Alice and Bob share the Bell-pair $\ket{B_{00}}$.
\item Alice encodes the two-bit string \mbox{$x\in\{0,1\}^2$} into a choice of the four possible Bell-pairs.
\item Alice prepares the respective Bell-pair using operations local to only her half of the shared state ($\hat{\mathbb{I}}$, $\hat{X}$, $\hat{Z}$ or \mbox{$\hat{Z}\hat{X}$}).
\item Alice sends her qubit to Bob.
\item Bob measures in the Bell basis, with four possible measurement outcomes.
\item The measurement outcome corresponds to the bit-string $x$.
\item $\Box$
\end{enumerate}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
\lstick{x_0} & \cw & \cw & \control \cw \\
\lstick{x_1} & \cw & \control \cw \\
\lstick{} & \qw & \gate{X} \cwx & \gate{Z} \cwx[-2] & \qw & \multimeasureD{1}{\text{Bell}} & \cw & \rstick{x_0} \\
\lstick{} & \qw & \qw & \qw & \qw & \ghost{\text{Bell}} & \cw & \rstick{x_1}
\inputgroupv{3}{4}{.8em}{.8em}{\ket{B_{00}}\quad} \\
} \nonumber
\end{align}
}
\end{mdframed}
\caption{Superdense coding protocol for communicating two classical bits via transmission of a single qubit. The protocol requires the two parties share a Bell-pair as a resource, provided by a third party.} \label{alg:superdense}
\end{table}
